---
title: "Data Mining Project"
author: "Varsha Rajasekar"
date: "5/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(caret)
library(data.table)
library(kableExtra)
library(lubridate)
library(Matrix.utils)
library(DT)
library(wordcloud) 
library(RColorBrewer) 
library(ggthemes) 
library(irlba)
library(recommenderlab)
library(recosystem)
library(h2o)
```

```{r}
# Ratings dataset
ratings <- read_csv("/Users/varsharajasekar/Downloads/ml-latest-small/ratings.csv")

glimpse(ratings)

```




```{r}
#Movies dataset
movies <- read_csv("/Users/varsharajasekar/Downloads/ml-latest-small/movies.csv")
glimpse(movies)
movies

```



```{r}
# Tags dataset
tags <- read_csv("/Users/varsharajasekar/Downloads/ml-latest-small/tags.csv")
glimpse(tags)

tags
summary(tags)
```


```{r}
#Combining ratings and movies dataset
movielens <- merge(ratings,movies,by=c("movieId"))

summary(movielens)
head(movielens,10)
```


```{r}
set.seed(42)
partition <- createDataPartition(y = movielens$rating, p = 0.6, list = F)
training <-  movielens[partition, ]
validation <- movielens[-partition, ]
```

### PART A: Regression
```{r}
# Movie effect

# Calculate the average of all ratings 
mu <- mean(training$rating)

# Calculate Beta_m 
movie_effect <- training %>% 
  group_by(movieId) %>% 
  summarize(Bm = mean(rating - mu))

# Predict ratings
pred_Bm <- mu + validation %>% 
  left_join(movie_effect, by='movieId') %>%
  .$Bm


# Movie + User effect

# Calculate Beta_u  
user_effect <- training %>%  
  left_join(movie_effect, by='movieId') %>%
  group_by(userId) %>%
  summarize(Bu = mean(rating - mu - Bm))

# Predict ratings
pred_Bu <- validation %>% 
  left_join(movie_effect, by='movieId') %>%
  left_join(user_effect, by='userId') %>%
  mutate(pred = mu + Bm + Bu) %>%
  .$pred


# Movie + User + Time effect
   
# Calculate Beta_t 
time_effect <- training %>%
  left_join(movie_effect, by='movieId') %>%
  left_join(user_effect, by='userId') %>%
  mutate(date = round_date(as_datetime(timestamp), unit = "week")) %>%
  group_by(date) %>%
  summarize(Bt = mean(rating - mu - Bm - Bu))

 
# Predicted ratings
valid <- validation %>%
  mutate(date = round_date(as_datetime(timestamp), unit = "week"))

pred_Bt <- valid %>%
  left_join(movie_effect, by='movieId') %>%
  left_join(user_effect, by='userId') %>%
  left_join(time_effect, by='date') %>%
  mutate(pred = mu + Bm + Bu + Bt) %>%
  .$pred

```

```{r}
rmse_Bm <- RMSE(validation$rating,pred_Bm)  
rmse_Bm
```

```{r}
rmse_Bu <- RMSE(validation$rating,pred_Bu)
rmse_Bu
```

```{r}
rmse_Bt <- RMSE(valid$rating,pred_Bt)
rmse_Bt
```


```{r}
# Regularization using lasso parameter

lambdas <- seq(0, 10, 0.25)
  
  rmses <- sapply(lambdas, function(l){
    
    mu_reg <- mean(training$rating)
    
    Bm_reg <- training %>% 
      group_by(movieId) %>%
      summarize(Bm_reg = sum(rating - mu_reg)/(n()+l))
    
    Bu_reg <- training %>% 
      left_join(Bm_reg, by="movieId") %>%
      group_by(userId) %>%
      summarize(Bu_reg = sum(rating - Bm_reg - mu_reg)/(n()+l))
    
    rating_pred <- 
      validation %>% 
      left_join(Bm_reg, by = "movieId") %>%
      left_join(Bu_reg, by = "userId") %>%
      mutate(pred = mu_reg + Bm_reg + Bu_reg) %>%
      .$pred
    
    return(RMSE(validation$rating,rating_pred))
  })
```

```{r}
#For the full model, the optimal  λ is:
    
lambda <- lambdas[which.min(rmses)]
lambda
```

```{r}
rmse_reg <- min(rmses)
rmse_reg
```

```{r}
rmse_regression <- data.frame(Methods=c("movie effect","movie + user effects","movie + user + time effects","Regularized Movie + User Effect"),RMSE = c(rmse_Bm, rmse_Bu,rmse_Bt,rmse_reg))

kable(rmse_regression) %>%
  kable_styling(bootstrap_options = "striped" , full_width = F , position = "center") %>%
  kable_styling(bootstrap_options = "bordered", full_width = F , position ="center") %>%
  column_spec(1,bold = T ) %>%
  column_spec(2,bold =T )
```



### PART B: Recommender Engines
```{r}

train1 <- movielens %>% 
  mutate(userId = as.factor(movielens$userId)) %>% 
  mutate(movieId = as.factor(movielens$movieId))

train1$userId <- as.numeric(train1$userId)
train1$movieId <- as.numeric(train1$movieId)

sparse_mat_rating <- sparseMatrix(i = train1$userId,
                         j = train1$movieId ,
                         x = train1$rating, 
                         dims = c(length(unique(train1$userId)),
                                  length(unique(train1$movieId))),  
                         dimnames = list(paste("u", 1:length(unique(train1$userId)), sep = ""), 
                                        paste("m", 1:length(unique(train1$movieId)), sep = "")))

rm(train1)

```

```{r}
#Convert rating matrix into a recommenderlab sparse matrix
rating_matrix <- new("realRatingMatrix", data = sparse_mat_rating)
rating_matrix
```

```{r}
# Cosine similarity for users

users_sim_mat <- similarity(rating_matrix[1:50,], 
                               method = "cosine", 
                               which = "users")

image(as.matrix(users_sim_mat), main = "User similarity")



# Cosine similarity for movies

movies_sim_mat <- similarity(rating_matrix[,1:50], 
                               method = "cosine", 
                               which = "items")

image(as.matrix(movies_sim_mat), main = "Movies similarity")
```

```{r}
# Minimum number of movies per user
min_n_movies <- quantile(rowCounts(rating_matrix), 0.9)
print(min_n_movies)

# Minimum number of users per movie
min_n_users <- quantile(colCounts(rating_matrix), 0.9)
print(min_n_users)

# Selecting users and movies according to the above criterion
ratings <- rating_matrix[rowCounts(rating_matrix) > min_n_movies,
                            colCounts(rating_matrix) > min_n_users]
ratings
```

#### Using cross-validation to validate models

We will The k-fold cross-validation approach since is the most accurate one, although it's computationally heavier. 

Using this approach, we split the data into some chunks, take a chunk out as the test set, and evaluate the accuracy. Then, we can do the same with each other chunk and compute the average accuracy.  

For each user in the test set, we need to define how many items to use to generate recommendations. For this, I first check the minimum number of items rated by users to be sure there will be no users with no items to test.

```{r k-fold, message=FALSE, warning=FALSE}
min(rowCounts(rating_matrix))
items_to_keep <- 10 #number of items to generate recommendations
rating_threshold <- 4 # threshold with the minimum rating that is considered good

n_fold <- 10
eval_sets <- evaluationScheme(data = ratings, 
                              method = "cross-validation",
                              k = n_fold, 
                              given = items_to_keep, 
                              goodRating = rating_threshold)
size_sets <- sapply(eval_sets@runsTrain, length)
size_sets
```

Using ten-fold approach, we get ten sets of the same size 54.

#### UBCF Model

Let's have a look at the default parameters of IBCF model.  
nn: number of similar users
Method: similarity funtion, which is Cosine by default, may also be pearson. 

```{r UBCF default parameters}
recommender_models <- recommenderRegistry$get_entries(dataType ="realRatingMatrix")
recommender_models$UBCF_realRatingMatrix$parameters
```

We have a parameter nn which we need to vary and check for the optimized model based on precision and recall. We will the cross validation sets which we generated earlier for better results. 

```{r Parameters tuning for UBCF method, message=FALSE}
# UBCF takes account of the nn-number of similar users. I will explore values, ranging between 5 and 75, in order to tune this parameter:
vector_nn <- c(5, 10, 20, 30, 40, 50, 60, 75)
models_to_evaluate <- lapply(vector_nn, function(nn){
  list(name = "UBCF",
       param = list(method = "cosine", nn = nn))
})
names(models_to_evaluate) <- paste0("UBCF_k_", vector_nn)

#Now I build and evaluate the same UBCF models with different values of the nn-number of similar users.
n_recommendations <- c(1, 5, seq(10, 100, 10))
list_results <- evaluate(x = eval_sets, 
                         method = models_to_evaluate, 
                         n = n_recommendations)
plot(list_results, annotate = 1, legend = "topleft") 
title("ROC curve")
plot(list_results, "prec/rec", annotate = 1, legend = "bottomright")
title("Precision-recall")
```

Based on both the graphs we can say that the UBCF model with nn=50 performs better. We will use nn=50 to build the model.

#### IBCF Method
Let's have a look at the default parameters of IBCF model.  
k: number of items to compute the similarities.
Method: similarity funtion, which is Cosine by default, may also be pearson. 

```{r UBCF default parameters}
recommender_models <- recommenderRegistry$get_entries(dataType ="realRatingMatrix")
recommender_models$IBCF_realRatingMatrix$parameters
```

```{r Parameters tuning for IBCF method}
# IBCF takes account of the k-closest items. I will explore values, ranging between 5 and 50, in order to tune this parameter:
vector_k <- c(5, 10, 15, 20, 25, 30, 40, 50)
models_to_evaluate <- lapply(vector_k, function(k){
  list(name = "IBCF",
       param = list(method = "cosine", k = k))
})
names(models_to_evaluate) <- paste0("IBCF_k_", vector_k)

#Now I build and evaluate the same IBCF/cosine models with different values of the k-closest items:
n_recommendations <- c(1, 5, 10, 20, 25, 30, 40, 50)
list_results <- evaluate(x = eval_sets, 
                         method = models_to_evaluate, 
                         n = n_recommendations)
plot(list_results, annotate = 1, legend = "topleft") 
title("ROC curve")
plot(list_results, "prec/rec", annotate = 1, legend = "bottomright")
title("Precision-recall")
```

From both the graphs we can see that k=15 performs well over the course for different number of reccomendations.

#### Comparing algorithms

We will compare both UBCF and IBCF models but we will also include two other basic models. Those are popular method based and random method based.  

In popular method based model we predict/recommend movies based on the most popular movies and in random method based model we recommend movies randomly.

First we will comparing these models on precision, recall etc

```{r}
algorithms <- list( "random items" = list(name="RANDOM", param=NULL), 
                    "popular items" = list(name="POPULAR", param=NULL),
                    "user-based CF" = list(name="UBCF", param=list(nn=50)),
                    "item-based CF" = list(name="IBCF", param=list(k=15))
)

results <- evaluate(eval_sets, algorithms,type = "topNList", n=c(1,3,5,10,15,20))
plot(results, annotate=c(1,3), legend="bottomright")
plot(results, "prec/rec", annotate=3, legend="topleft")
```

From both the models we can see that popular method based and UBCF models performing well.

Next we compare them based on movie ratings prediction.

```{r Builiding and testing popular method model}
set.seed(1)
train2 <- evaluationScheme(ratings, method="split",train=0.7, given=10, goodRating = 4)

# Popular method
popular_model <- Recommender(getData(train2, "train"), "POPULAR",param=list(normalize = "center"))
popular_pred <- predict(popular_model, getData(train2, "known"), type="ratings")
rmse_popular <- calcPredictionAccuracy(popular_pred, getData(train2, "unknown"))

# Random method
random_model <- Recommender(getData(train2, "train"), "RANDOM",param=list(normalize = "center"))
random_pred <- predict(random_model, getData(train2, "known"), type="ratings")
rmse_random <- calcPredictionAccuracy(random_pred, getData(train2, "unknown"))

# UBCF method
ubcf_model <- Recommender(getData(train2, "train"), method = "UBCF", 
                     param=list(normalize = "center", method="Cosine", nn=50))
ubcf_pred <- predict(ubcf_model, getData(train2, "known"), type="ratings")
rmse_ubcf <- calcPredictionAccuracy(ubcf_pred, getData(train2, "unknown"))

# IBCF method
ibcf_model <- Recommender(getData(train2, "train"), method = "IBCF", 
                          param=list(normalize = "center", method="Cosine", k=15))
ibcf_pred <- predict(ibcf_model, getData(train2, "known"), type="ratings")
rmse_ibcf <- calcPredictionAccuracy(ibcf_pred, getData(train2, "unknown"))
rmse_ibcf

rmse_recommender <- data.frame(methods=c("Popularity Model", "Random Model","UBCF Model","IBCF Model"),
                               rmse = c(rmse_popular[1],rmse_random[1],rmse_ubcf[1],rmse_ibcf[1]),
                               mse = c(rmse_popular[2],rmse_random[2],rmse_ubcf[2],rmse_ibcf[2]),
                               mae = c(rmse_popular[3],rmse_random[3],rmse_ubcf[3],rmse_ibcf[3]))

kable(rmse_recommender) %>%
  kable_styling(bootstrap_options = "striped" , full_width = F , position = "center") %>%
  kable_styling(bootstrap_options = "bordered", full_width = F , position ="center") %>%
  column_spec(1,bold = T )
```

As you can see, again both popular method based and UBCF models perform well. But UBCF has an advantage that it recommends different movies to users based on them, whereas popular method based recommends same movies to all the users.


### PART C: Tree Based Methods
```{r}
train3 <- training

# Creating new columns for number of movies each user rated and number of users that rated each movie

train3 <- train3 %>%
            group_by(userId) %>%
            mutate(movies_per_user = n())

train3 <- train3 %>%
  group_by(movieId) %>%
  mutate(users_per_movie = n())

train3$userId <-  as.factor(train3$userId)
train3$movieId <- as.factor(train3$movieId)
train3

valid <- validation  

valid <- valid %>%
  group_by(userId) %>%
  mutate(movies_per_user = n())

valid <- valid %>%
  group_by(movieId) %>%
  mutate(users_per_movie = n())

valid$userId  <- as.factor(valid$userId)
valid$movieId <- as.factor(valid$movieId)

```


```{r}
# connect to H2O instance 
h2o.init(
 nthreads=-1,                   
 max_mem_size = "16G")
h2o.removeAll()

```

```{r}
#partitioning 
splits <- h2o.splitFrame(as.h2o(train3), 
                         ratios = 0.7, 
                         seed = 1)
```

```{r}
train <- splits[[1]]
test <- splits[[2]]
```

```{r}
#clear unusued memory
invisible(gc())

#remove progress bar
h2o.no_progress()

gbm_default <- h2o.gbm( x = c("movieId","userId","movies_per_user","users_per_movie") ,
           y = "rating" , 
           training_frame = train ,
           nfolds = 5,
           )

gbm_default

```

```{r}
# Performing 5-fold cross-validation
gbm_model1 <- h2o.gbm( x = c("movieId","userId","movies_per_user","users_per_movie") ,
           y = "rating" , 
           training_frame = train ,
           nfolds = 5,
           ntrees = 100,
           stopping_rounds = 10,
           stopping_tolerance = 0,
           seed = 123,
           keep_cross_validation_predictions = TRUE,
           fold_assignment = "Random")

gbm_model1

```

```{r}
# Performing 10-fold cross-validation
gbm_model2 <- h2o.gbm( x = c("movieId","userId","movies_per_user","users_per_movie") ,
           y = "rating" , 
           training_frame = train ,
           nfolds = 10,
           ntrees = 100,
           stopping_rounds = 10,
           stopping_tolerance = 0,
           seed = 123,
           keep_cross_validation_predictions = TRUE,
           fold_assignment = "Random")

gbm_model2
```


```{r}
# Reduced learn_rate to 0.05
gbm_model3 <- h2o.gbm( x = c("movieId","userId","movies_per_user","users_per_movie") ,
           y = "rating" , 
           training_frame = train ,
           nfolds = 5,
           ntrees = 100,
           learn_rate=0.05,
           stopping_rounds = 10,
           stopping_tolerance = 0,
           seed = 123,
           keep_cross_validation_predictions = TRUE,
           fold_assignment = "Random")

gbm_model3

```

```{r}
rmse_default <- h2o.rmse(gbm_default, xval = TRUE)
rmse_model1 <-  h2o.rmse(gbm_model1, xval = TRUE)
rmse_model2 <-  h2o.rmse(gbm_model2, xval = TRUE)
rmse_model3 <-  h2o.rmse(gbm_model3, xval = TRUE)
```

```{r}
mae_default <- h2o.mae(gbm_default, xval = TRUE)
mae_model1 <-  h2o.mae(gbm_model1, xval = TRUE)
mae_model2 <-  h2o.mae(gbm_model2, xval = TRUE)
mae_model3 <-  h2o.mae(gbm_model3, xval = TRUE)
```

```{r}
r2_default <- h2o.r2(gbm_default, xval = TRUE)
r2_model1 <-  h2o.r2(gbm_model1, xval = TRUE)
r2_model2 <-  h2o.r2(gbm_model2, xval = TRUE)
r2_model3 <-  h2o.r2(gbm_model3, xval = TRUE)
```

```{r}
deviance_default <- h2o.mean_residual_deviance(gbm_default, xval = TRUE)
deviance_model1 <-  h2o.mean_residual_deviance(gbm_model1, xval = TRUE)
deviance_model2 <-  h2o.mean_residual_deviance(gbm_model2, xval = TRUE)
deviance_model3 <-  h2o.mean_residual_deviance(gbm_model3, xval = TRUE)
```

```{r}
perf_gbm <- data.frame(methods=c("Default","Model 1","Model 2","Model 3"),RMSE = c(rmse_default,rmse_model1,rmse_model2,rmse_model3), MAE=c(mae_default,mae_model1,mae_model2,mae_model3), R2=c(r2_default,r2_model1,r2_model2,r2_model3))

kable(perf_gbm) %>%
  kable_styling(bootstrap_options = "striped" , full_width = F , position = "center") %>%
  kable_styling(bootstrap_options = "bordered", full_width = F , position ="center")
```

```{r}
results_cv <- function(h2o_model) {
  h2o_model@model$cross_validation_metrics_summary %>% 
    as.data.frame() %>% 
    select(-mean, -sd) %>% 
    t() %>% 
    as.data.frame() %>% 
    mutate_all(as.character) %>% 
    mutate_all(as.numeric) %>% 
    select(RMSE = rmse, 
           MAE = mae,
           R2 = r2) %>% 
    return()
  }

# Use function: 
results_cv(gbm_model2) -> model

# Model Performance by Graph: 
theme_set(theme_minimal())

plot_results <- function(df_results) {
  df_results %>% 
  gather(Metrics, Values) %>% 
  ggplot(aes(Metrics, Values, fill = Metrics, color = Metrics)) +
  geom_boxplot(alpha = 0.3, show.legend = FALSE) + 
  theme(plot.margin = unit(c(1, 1, 1, 1), "cm")) +    
  scale_y_continuous(labels = scales::percent) + 
  facet_wrap(~ Metrics, scales = "free") + 
  labs(title = "Model Performance: Gradient Boosting Machine", y = NULL)
  }

plot_results(model) 
```


```{r}
#i predict ratings on validation set and evaluate RMSE
gbm_pred <- h2o.predict(gbm_model2,as.h2o(valid))

rmse_gbm <- RMSE(gbm_pred, as.h2o(valid$rating))
rmse_gbm
```

```{r}
#clear unusued memory
invisible(gc())
#remove bar progress
h2o.no_progress()

# Default rf model 
rf_default <- h2o.randomForest(        
  training_frame = train,       
  x= c("movieId" ,"userId" ,"timestamp", "movies_per_user","users_per_movie"),        
  y= "rating",                         
  nfolds=5
)

summary(rf_default)
```

```{r}
rf_model1 <- h2o.randomForest(        
   training_frame = train,       
   x= c("movieId" ,"userId", "movies_per_user","users_per_movie"),                      
   y= "rating",                         
   ntrees = 100,
   nfolds = 5,
   stopping_rounds = 10,
   stopping_tolerance = 0,
   seed=123,
   keep_cross_validation_predictions = TRUE,
   fold_assignment = "Random")
 
 summary(rf_model1)
```

```{r}
rf_model2 <- h2o.randomForest(        
   training_frame = train,       
   x= c("movieId" ,"userId", "movies_per_user","users_per_movie"),                      
   y= "rating",                         
   ntrees = 100,
   nfolds = 10,
   stopping_rounds = 10,
   stopping_tolerance = 0,
   seed=123,
   keep_cross_validation_predictions = TRUE,
   fold_assignment = "Random")
 
 summary(rf_model2)
```

```{r}
rf_model3 <- h2o.randomForest(        
  training_frame = train,       
  x= c("movieId" ,"userId","movies_per_user","users_per_movie"),                      
  y= "rating", 
  nfolds=10,
  ntrees=100,
  max_depth = 10,
  stopping_rounds = 10,
  stopping_tolerance = 0,
  seed=123,
  keep_cross_validation_predictions = TRUE,
  fold_assignment = "Random")

summary(rf_model3)
```


```{r}
rmse_default <- h2o.rmse(rf_default, xval = TRUE)
rmse_model1 <-  h2o.rmse(rf_model1, xval = TRUE)
rmse_model2 <-  h2o.rmse(rf_model2, xval = TRUE)
rmse_model3 <-  h2o.rmse(rf_model3, xval = TRUE)
```

```{r}
mae_default <- h2o.mae(rf_default, xval = TRUE)
mae_model1 <-  h2o.mae(rf_model1, xval = TRUE)
mae_model2 <-  h2o.mae(rf_model2, xval = TRUE)
mae_model3 <-  h2o.mae(rf_model3, xval = TRUE)
```

```{r}
r2_default <- h2o.r2(rf_default, xval = TRUE)
r2_model1 <-  h2o.r2(rf_model1, xval = TRUE)
r2_model2 <-  h2o.r2(rf_model2, xval = TRUE)
r2_model3 <-  h2o.r2(rf_model3, xval = TRUE)
```

```{r}
deviance_default <- h2o.mean_residual_deviance(rf_default, xval = TRUE)
deviance_model1 <-  h2o.mean_residual_deviance(rf_model1, xval = TRUE)
deviance_model2 <-  h2o.mean_residual_deviance(rf_model2, xval = TRUE)
deviance_model3 <-  h2o.mean_residual_deviance(rf_model3, xval = TRUE)
```

```{r}
perf_rf <- data.frame(Models=c("Default","Model 1","Model 2","Model 3"),RMSE = c(rmse_default,rmse_model1,rmse_model2,rmse_model3), MAE=c(mae_default,mae_model1,mae_model2,mae_model3), R2=c(r2_default,r2_model1,r2_model2,r2_model3))

kable(perf_rf) %>%
  kable_styling(bootstrap_options = "striped" , full_width = F , position = "center") %>%
  kable_styling(bootstrap_options = "bordered", full_width = F , position ="center")
```

```{r}
# We select model2 since it has the least rmse for 10 fold cross validation
results_cv <- function(h2o_model) {
  h2o_model@model$cross_validation_metrics_summary %>% 
    as.data.frame() %>% 
    select(-mean, -sd) %>% 
    t() %>% 
    as.data.frame() %>% 
    mutate_all(as.character) %>% 
    mutate_all(as.numeric) %>% 
    select(RMSE = rmse, 
           MAE = mae,
           R2 = r2) %>% 
    return()
  }

# Use function: 
results_cv(rf_model3) -> model

# Model Performance by Graph: 
theme_set(theme_minimal())

plot_results <- function(df_results) {
  df_results %>% 
  gather(Metrics, Values) %>% 
  ggplot(aes(Metrics, Values, fill = Metrics, color = Metrics)) +
  geom_boxplot(alpha = 0.3, show.legend = FALSE) + 
  theme(plot.margin = unit(c(1, 1, 1, 1), "cm")) +    
  scale_y_continuous(labels = scales::percent) + 
  facet_wrap(~ Metrics, scales = "free") + 
  labs(title = "Model Performance: Random Forest", y = NULL)
  }

plot_results(model) 
```


```{r}
# Predict ratings on validation set 
rf_pred <- h2o.predict(rf_model3,as.h2o(valid))

rmse_rf <- RMSE(rf_pred, as.h2o(valid$rating))
rmse_rf
```

```{r}
# Stacked Ensemble : take the best two previous models (gbdt_3 and rf_3)

ensemble_model <- h2o.stackedEnsemble(x = c("movieId" ,"userId","movies_per_user","users_per_movie"),
                                y = "rating",
                                training_frame = train,
                                model_id = "my_ensemble_auto",
                                base_models = list(gbm_model2@model_id, rf_model3@model_id))

# Predict ratings on validation set
ensemble_pred <- h2o.predict(ensemble_model,as.h2o(valid))

rmse_ensemble <- RMSE(ensemble_pred, as.h2o(valid$rating))
rmse_ensemble
```

```{r}
rmse_ensemble_methods <- data.frame(Methods=c("gradient Boosting","random forest","stacked ensemble"),RMSE = c(rmse_gbm, rmse_rf, rmse_ensemble))

kable(rmse_ensemble_methods) %>%
  kable_styling(bootstrap_options = "striped" , full_width = F , position = "center") %>%
  kable_styling(bootstrap_options = "bordered", full_width = F , position ="center") 
```

```{r}
rmse_results <- data.frame(methods=c("Movie Effect","Movie + User Effects","Movie + User + Time Effects","Regularized Movie + User Effect","Popularity Model", "Random Model","UBCF Model","IBCF Model","Gradient Boosting","Random Forest","Stacked Ensemble"),rmse = c(rmse_Bm, rmse_Bu,rmse_Bt,rmse_reg,rmse_popular[1],rmse_random[1],rmse_ubcf[1],rmse_ibcf[1],rmse_gbm, rmse_rf, rmse_ensemble))

kable(rmse_results) %>%
  kable_styling(bootstrap_options = "striped" , full_width = F , position = "center") %>%
  kable_styling(bootstrap_options = "bordered", full_width = F , position ="center") %>%
  column_spec(1,bold = T ) %>%
  column_spec(2,bold = T )
```


```{r}
#remove objects
rm(train3,valid)

```



